---
title: "Local Moran Plot"
author: "Dr. Adams"
date: '2018-02-23'
output: html_document
---

# Example of Local Moran's I hotspot map in R

This is a demo of using the plot.local.moran() function on Hamilton, ON average house value by census tract in 2016. The data has been modified for an assignment in UTM's GGR376. Do not use the data for research purposes.

### Load libraries and source the functions
```{r}
library(rgdal)
library(spdep)
library(RColorBrewer) # Not required for the plot.local.moran()

# Load plot.local.moran function
source("https://raw.githubusercontent.com/gisUTM/spatialplots/master/plotlocalmoran.R")
```


## Read in GEOJSON of House Values
```{r}
hamilton <- readOGR("https://raw.githubusercontent.com/gisUTM/GGR376/master/Lab_1/houseValues.geojson")
```

View a plot of the house values.

```{r}
# Colour palette
col.pal <- brewer.pal(7, name = "BuPu")

spplot(hamilton,
       "houseValue",
       col.regions = col.pal, # Use the color palette
       cuts = 6, # Set the number of classes n (brewer.pa) - 1
       col = "transparent") # Polygon borders
```

Create a neighbours list.

```{r}
ham.nb <- poly2nb(hamilton)
```

Convert neighbours list to spatial weights.

```{r}
ham.wt <- nb2listw(ham.nb)
```

# Calculate Local Moran's

```{r}
ham.lmi <- localmoran(hamilton@data$houseValue, ham.wt)
```

# Plot Local Moran's I
```{r}
plot.local.moran(hamilton, variable.name = "houseValue", weights = ham.wt, local.moran = ham.lmi, legend.location = "topright")
```

